Using R to help plan the <br> future of transport

### 2019-01-14 ms-meetup-nov18.Rmd
no vertical scroll on slides

```{r ms-mapdeck, eval = FALSE}
library (mapdeck)
fm$flow <- 20 * fm$flow / max (fm$flow)
pal <- colorRampPalette (c ("lawngreen", "red"))
loc <- as.numeric(apply (sf::st_coordinates (ms$osm_lines), 2, mean)) [1:2]
mapdeck (style = 'mapbox://styles/mapbox/dark-v9',
         zoom = 12,
         location = loc) %>%
    add_line (data = fm,
              layer_id = "ms-highways",
              origin = c("from_lon", "from_lat"),
              destination = c("to_lon", "to_lat"),
              stroke_colour = "flow",
              stroke_width = "flow",
              palette = pal)
```
```{r ms-mapdeck-fakey, echo = FALSE}
loc <-  c (7.619786, 51.952610)
```

@@

```{r promenade-reweight, eval = FALSE}
shorter <- 0.1
g <- weight_streetnet (ms$osm_lines, wt_profile = "bicycle")
index <- which (g$way_id %in% ids_prom)
g$d_weighted [index] <- g$d [index] * (1 - shorter) #<<
f <- dodgr_flows_aggregate (g, from = pts, to = pts,
                            flows = flowmat)
```

>>>>

```{r ms-mapdeck, eval = FALSE}
library (mapdeck)
fm$flow <- 20 * fm$flow / max (fm$flow)
pal <- colorRampPalette (c ("lawngreen", "red"))
loc <- apply (sf::st_coordinates (ms$osm_lines), 2, mean) [1:2]
mapdeck (style = 'mapbox://styles/mapbox/dark-v9',
         zoom = 12,
         location = as.numeric(loc)) %>%
    add_line (data = fm,
              layer_id = "ms-highways",
              origin = c("from_lon", "from_lat"),
              destination = c("to_lon", "to_lat"),
              stroke_colour = "flow",
              stroke_width = "flow",
              palette = pal)
```
```{r ms-mapdeck-fakey, echo = FALSE}
loc <-  c (7.619786, 51.952610)
```

@@

```{r promenade-reweight, eval = FALSE}
shorter <- 0.1
g <- weight_streetnet (ms$osm_lines, wt_profile = "bicycle")
index <- which (g$way_id %in% ids_prom)
g$d_weighted [index] <- g$d [index] * (1 - shorter) #<<
flow_mat <- matrix (1, nrow = 1000, ncol = 1000)
f <- dodgr_flows_aggregate (g, from = pts, to = pts,
                            flows = flow_mat)
```
